Convex Surrogates via Polyhedral Losses

### 2019-05-01 neurips-19/cvx-fin.tex
Jessie adding more to and organizing lit review

\subsection{Jessie's lit review}
\begin{itemize}
	\item Structured prediction: Structured hinge loss.
	``Direct loss minimization for structured prediction'' by McAllester et al. \url{https://papers.nips.cc/paper/4069-direct-loss-minimization-for-structured-prediction.pdf}
	From my understanding, structured hinge isn't necessarily polyhedral, but seems like it can be, depending on the weight function and joint feature function (JFF).
	In practice, my guess is that the JFF is rarely, if ever, linear, though.

@@

	 \item \url{http://jmlr.csail.mit.edu/papers/volume5/zhang04b/zhang04b.pdf} Section 4 in general might be handy, asmight Appendix A.
	 \jessie{I think this one might be one of our best shots at an example.}

	 \item To read: \url{http://www.jmlr.org/papers/volume10/rudin09b/rudin09b.pdf}

>>>>

\subsection{Jessie's lit review}
General ``properties'' that might be of value for referencing, but I couldn't find any polyhedral losses associated with them:
\begin{itemize}
	\item Discounted Cumulative Gain (DCG)
	\item Structured prediction (structured hinge, see below)
	\item Regret and refine multiclass classification
	\item Wilcoxan statistic mentioned below
	\item Full and partial ranking
\end{itemize}

Papers and notes listed here:
\begin{itemize}
	\item Structured prediction: Structured hinge loss.
	``Direct loss minimization for structured prediction'' by McAllester et al. \url{https://papers.nips.cc/paper/4069-direct-loss-minimization-for-structured-prediction.pdf}
	From my understanding, structured hinge isn't necessarily polyhedral, but seems like it can be, depending on the weight function and joint feature function (JFF).
	In practice, my guess is that the JFF is rarely, if ever, linear, though.

@@

	 \item \url{http://jmlr.csail.mit.edu/papers/volume5/zhang04b/zhang04b.pdf} Section 4 in general might be handy, as might Appendix A.
	 \jessie{I think this one might be one of our best shots at an example.}

	 \item \url{http://www.jmlr.org/papers/volume10/rudin09b/rudin09b.pdf} heavily cites

	 \item \url{https://amstat.tandfonline.com/doi/pdf/10.1198/jcgs.2010.08115?needAccess=true} and \url{https://www.tau.ac.il/~saharon/papers/pwl-long1.pdf} focus on generalizations of hinge loss, but typically the quantile loss.
	 The latter also includes some ``almost quadratic'' losses, but are kind of the opposite of what we want; quadratic in the convex hull of embedded reports and linear outside.
